Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''

### 2019-05-21 tex/v3/section_1_introduction.tex
change intro
Ref with chicago style

\rev{In this paper, we propose a novel technique for accelerating the Sinkhorn algorithm when computing regularized OT distance between discrete measures. Our idea
is strongly related to a screening strategy when solving a \emph{Lasso}
problem in sparse supervised learning \citep{Ghaoui2010SafeFE}. Based on the fact
that a  transport plan resulting from an OT problem is sparse or presents a large
number of neglectable values \citep{blondel2018ICML}, our objective is to identify the  dual variables of an approximate Sinkhorn problem, that are smaller than a predefined threshold, and thus that can be safely removed before optimization.  
Within this global context, our contributions are the following :
\begin{itemize}
	\item From a methodological point of view, we propose a reformulation the dual of the Sinkhorn divergence problem by imposing variables to be larger than a threshold.
	This formulation allows us to introduce sufficient conditions, computable beforehand, for a variable to be strictly satisfied its constraint, leading then to
	a ``screened'' version of the dual of Sinkhorn divergence. 
	\item We provide some theoretical analysis of the solution of the ``screened''  Sinkhorn divergence, showing that its objective value and the marginal constraint satisfaction are properly controlled 	as the number of screened variables decreases.
	\item From an algorithmic standpoint, we use a constrained LBFGS algorithm \cite{nocedal1980,byrd1995L-BFGS-B} but provide a careful analysis of the lower bound and upper bound of the dual	variables, resulting in a well-posed and efficient algorithm denoted as \emph{Screenkhorn}.
	\item Our empirical analysis depicts how the approach behaves in a simple Sinkhorn divergence computation context. When considered in  complex machine learning
	pipelines, we show that \emph{Screenkhorn} can lead to strong gain in efficiency
	while not compromising on accuracy.
\end{itemize}}
%	
%
%These constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
%We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
%Furthermore, the active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
%We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
%Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained box-constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,byrd1995L-BFGS-B} that relies on an estimation of the inverse of the Hessian based on gradients differences. 
%L-BFGS-B algorithm was adapted to the OT setting via the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.}

>>>>

{In this paper, we propose a novel technique for accelerating the Sinkhorn algorithm when computing regularized OT distance between discrete measures. Our idea
is strongly related to a screening strategy when solving a \emph{Lasso}
problem in sparse supervised learning \citep{Ghaoui2010SafeFE}. Based on the fact
that a  transport plan resulting from an OT problem is sparse or presents a large
number of neglectable values \citep{blondel2018ICML}, our objective is to identify the  dual variables of an approximate Sinkhorn problem, that are smaller than a predefined threshold, and thus that can be safely removed before optimization.  
Within this global context, our contributions are the following :
\begin{itemize}
	  \setlength\itemsep{-0.1cm}

	\item From a methodological point of view, we propose a reformulation the dual of the Sinkhorn divergence problem by imposing variables to be larger than a threshold.
	This formulation allows us to introduce sufficient conditions, computable beforehand, for a variable to be strictly satisfied its constraint, leading then to
	a ``screened'' version of the dual of Sinkhorn divergence. 
	\item We provide some theoretical analysis of the solution of the ``screened''  Sinkhorn divergence, showing that its objective value and the marginal constraint satisfaction are properly controlled 	as the number of screened variables decreases.
	\item From an algorithmic standpoint, we use a constrained LBFGS algorithm \cite{nocedal1980,byrd1995L-BFGS-B} but provide a careful analysis of the lower bound and upper bound of the dual	variables, resulting in a well-posed and efficient algorithm denoted as \emph{Screenkhorn}.
	\item Our empirical analysis depicts how the approach behaves in a simple Sinkhorn divergence computation context. When considered in  complex machine learning
	pipelines, we show that \emph{Screenkhorn} can lead to strong gain in efficiency
	while not compromising on accuracy.
\end{itemize}}
%	
%
%These constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
%We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
%Furthermore, the active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
%We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
%Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained box-constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,byrd1995L-BFGS-B} that relies on an estimation of the inverse of the Hessian based on gradients differences. 
%L-BFGS-B algorithm was adapted to the OT setting via the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.}

### 2019-05-21 tex/v3/section_3_algorithm.tex
new appendix
Ref with chicago style

The key idea of our approach is motivated by the so-called \emph{static screening test}~\cite{Ghaoui2010SafeFE} in supervised learning, which is a method able to quickly identify inactive features, i.e., features that have zero components in the solution vector. 
Then, these inactive features can be removed from the optimization problem to reduce its scale.
Before diving into detailed algorithmic analysis, let's us present a brief illustration of how we adapt static screening test to the dual of Sinkhorn divergence.
Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual} in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ correspond the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$. 
We also plot two lines correspond to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discard from the optimization procedure.

@@

\begin{lemma}
\label{lemma_actives_sets}
Let $(u^{*}, v^{*})$ be an optimal solution of the problem~\eqref{screen-sinkhorn}. 
Define
\begin{equation}
\label{I_epsilon_kappa_J_epsilon_kappa}
I_{\varepsilon,\kappa} = \big\{i=1, \ldots, n: \mu_i \geq \frac {\varepsilon^2} \kappa^{} r_i(K)\big\}, J_{\varepsilon,\kappa} = \big\{j=1, \ldots, m: \nu_j \geq \kappa{\varepsilon^2}{} c_j(K)\big\}
\end{equation}
Then one has $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ for all $i \in I^\complement_{\varepsilon,\kappa} $ and $j\in J^\complement_{\varepsilon,\kappa} .$
\end{lemma}

@@

Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ to the screened domain defined by $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where 
\begin{equation*}
\mathcal{U}_{\text{sc}} = \{u \in \R^{n_b}: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}\} \text{ and } \mathcal{V}_{\text{sc}} =\{v\in\R^{m_b}: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}.%, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
\end{equation*}
% and 
% \begin{equation*}
% 	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}. %, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
% \end{equation*}
where the vector comparison $\succeq$ has to be understood elementwise.
Now, we are ready to define the \emph{screened dual of Sinkhorn divergence} as
\begin{align}
\label{screen-sinkhorn_second_def}
\min_{u \in \mathcal{U}_{\text{sc}}, v \in \mathcal{V}_{\text{sc}}}\{\Psi_{\varepsilon, \kappa}(u,v)\}
\end{align}
where 
\begin{align*} 
\Psi_{\varepsilon,\kappa}(u, v) &= (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{v_{J_{\varepsilon,\kappa}}} + 
\varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\mathbf 1_{m_b} + \varepsilon \kappa^{-1} \mathbf 1_{n_b}^\top K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}}. %+ \Xi
\end{align*}
%with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.

@@

\begin{proposition}
\label{prop:bounds_of_usc_and_vsc}
Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def} and $K_{\min} = \min\limits_{i\in I_{\varepsilon,\kappa},j \in J_{\varepsilon,\kappa}}K_{ij}$. Then,
one has
\begin{equation}
\label{bound_on_u}
\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\varepsilon,\kappa}}\mu_i}{\varepsilon (m- m_b) + \varepsilon \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\kappa K_{\min}} m_b} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon K_{\min}},
\end{equation}
and
\begin{equation}
\label{bound_on_v}
\varepsilon\kappa \vee \frac{\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\varepsilon(n- n_b) + \varepsilon \vee \frac{\kappa\max_{i\in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon K_{\min} } n_b} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min} }
\end{equation}
for all $i\in I_{\varepsilon,\kappa}$ and $j\in J_{\varepsilon,\kappa}$.
\end{proposition}

\LinesNotNumbered
\begin{algorithm}[htbp]
\SetNlSty{textbf}{}{.}
\DontPrintSemicolon
\caption{Screenkhorn$(C,\eta,\mu,\nu,n_b,m_b)$}
\label{screenkhorn}
% \textbf{input: }{$C$, $\eta$, $\mu \in \Sigma_n$, $\nu \in \Sigma_m$, $n_b$ and $m_b$;}\\

@@

% \nl   $K \gets \exp(-C/\eta);$\\
\nl   $\xi \gets \mu \oslash r(K);$ \\
\nl   $\zeta \gets \nu \oslash c(K);$\\
\nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
\nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
\nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
\nl   $I_{\varepsilon,\kappa} \gets \{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\};$\\
\nl   $J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\

% \textbf{step 2:} \textcolor{black}{Bounds for L-BFGS}

% \nl   $K_{\min} \gets \min_{i \in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}K_{ij};$ \\
\nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
\nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \mu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \mu_i$; \\
\nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big), \bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
\nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big), \bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
\nl   $ \bar{\theta} \gets \text{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\ %\in \R^{n_b\times m_b}

@@

\nl  $u^{(0)} \gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
\nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
\nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
\nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
\nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\

% \textbf{step 4:} \textcolor{black}{Output}\\

\nl   {$u^{sc}_i \gets (\theta_u)_i$ if $i \in I_{\varepsilon,\kappa}$ and $u_i \gets \log(\varepsilon\kappa^{-1})$ if $i \in I^\complement_{\varepsilon,\kappa};$}\\
\nl   {$v^{sc}_j \gets (\theta_v)_j$ if $j \in J_{\varepsilon,\kappa}$ and $v_j \gets \log(\varepsilon\kappa)$ if $j \in J^\complement_{\varepsilon,\kappa};$}\\
\nl   \Return{$B(u^{\text{sc}},v^{\text{sc}})$.}
\end{algorithm}

>>>>

The key idea of our approach is motivated by the so-called \emph{static screening test}~\citep{Ghaoui2010SafeFE} in supervised learning, which is a method able to quickly identify inactive features, i.e., features that have zero components in the solution vector. 
Then, these inactive features can be removed from the optimization problem to reduce its scale.
Before diving into detailed algorithmic analysis, let's us present a brief illustration of how we adapt static screening test to the dual of Sinkhorn divergence.
Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w\in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual} in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ correspond the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$. 
We also plot two lines correspond to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discard from the optimization procedure.

@@

\begin{lemma}
\label{lemma_actives_sets}
Let $(u^{*}, v^{*})$ be an optimal solution of problem~\eqref{screen-sinkhorn}. 
Define
\begin{equation}
\label{I_epsilon_kappa_J_epsilon_kappa}
I_{\varepsilon,\kappa} = \big\{i=1, \ldots, n: \mu_i \geq \frac {\varepsilon^2} \kappa^{} r_i(K)\big\}, J_{\varepsilon,\kappa} = \big\{j=1, \ldots, m: \nu_j \geq \kappa{\varepsilon^2}{} c_j(K)\big\}
\end{equation}
Then one has $e^{u^{*}_i} = \varepsilon\kappa^{-1}$ and $e^{v^{*}_j} = \varepsilon\kappa$ for all $i \in I^\complement_{\varepsilon,\kappa} $ and $j\in J^\complement_{\varepsilon,\kappa} .$
\end{lemma}

@@

Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ to the screened domain defined by $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where 
\begin{equation*}
\mathcal{U}_{\text{sc}} = \{u \in \R^{n_b}: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}\} \text{ and } \mathcal{V}_{\text{sc}} =\{v\in\R^{m_b}: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}.%, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
\end{equation*}
% and 
% \begin{equation*}
% 	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}. %, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
% \end{equation*}
where the vector comparison $\succeq$ has to be understood elementwise.
Now, we are ready to define the \emph{screened dual of Sinkhorn divergence} as
\begin{align}
\label{screen-sinkhorn_second_def}
\min_{u \in \mathcal{U}_{\text{sc}}, v \in \mathcal{V}_{\text{sc}}}\{\Psi_{\varepsilon, \kappa}(u,v)\}
\end{align}
where 
\begin{align*} 
\Psi_{\varepsilon,\kappa}(u, v) &= (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{v_{J_{\varepsilon,\kappa}}} + 
\varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\mathbf 1_{m_b} + \varepsilon \kappa^{-1} \mathbf 1_{n_b}^\top K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}} + \Xi
\end{align*}
with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.

@@

\begin{proposition}
\label{prop:bounds_of_usc_and_vsc}
Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def} and $K_{\min} = \min\limits_{i\in I_{\varepsilon,\kappa},j \in J_{\varepsilon,\kappa}}K_{ij}$. Then,
one has
\begin{equation}
\label{bound_on_u}
\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\varepsilon,\kappa}}\mu_i}{\varepsilon (m- m_b) + \varepsilon \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\kappa K_{\min}} m_b} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon K_{\min}},
\end{equation}
and
\begin{equation}
\label{bound_on_v}
\varepsilon\kappa \vee \frac{\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\varepsilon(n- n_b) + \varepsilon \vee \frac{\kappa\max_{i\in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon K_{\min} } n_b} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min} }
\end{equation}
for all $i\in I_{\varepsilon,\kappa}$ and $j\in J_{\varepsilon,\kappa}$.
\end{proposition}
\LinesNotNumbered
\begin{algorithm}[htbp]
\SetNlSty{textbf}{}{.}
\DontPrintSemicolon
\caption{Screenkhorn$(C,\eta,\mu,\nu,n_b,m_b)$}
\label{screenkhorn}

@@

\nl   $\xi \gets \mu \oslash r(K);$ \\
\nl   $\zeta \gets \nu \oslash c(K);$\\
\nl   $\xi \gets \texttt{sort}(\xi);$ //(decreasing order)\\
\nl   $\zeta \gets \texttt{sort}(\zeta);$ //(decreasing order)\\
\nl   $\varepsilon \gets (\xi_{n_b}\zeta_{m_b})^{1/4}, \text{  } \kappa \gets \sqrt{{\zeta_{m_b}}/{\xi_{n_b}}}$;\\
\nl   $I_{\varepsilon,\kappa} \gets \{i=1, \ldots, n: \mu_i \geq {\varepsilon^2} \kappa^{-1} r_i(K)\};$\\
\nl   $J_{\varepsilon,\kappa} \gets \{j=1, \ldots, m: \nu_j \geq \varepsilon^2\kappa c_j(K)\};$\\ 
\nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
\nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \mu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \mu_i$; \\
\nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big), \bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
\nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big), \bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
\nl   $ \bar{\theta} \gets \text{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\

@@

\nl  $u^{(0)}\gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
\nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
\nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
\nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
\nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\
\nl   {$u^{sc}_i \gets (\theta_u)_i$ if $i \in I_{\varepsilon,\kappa}$ and $u_i \gets \log(\varepsilon\kappa^{-1})$ if $i \in I^\complement_{\varepsilon,\kappa};$}\\
\nl   {$v^{sc}_j \gets (\theta_v)_j$ if $j \in J_{\varepsilon,\kappa}$ and $v_j \gets \log(\varepsilon\kappa)$ if $j \in J^\complement_{\varepsilon,\kappa};$}\\
\nl   \Return{$B(u^{\text{sc}},v^{\text{sc}})$.}
\end{algorithm}
